
%%%
%  PMPlanPub.TeX (UTF-8 BOM)
%
%  人名已手动打码
%
%  编译文档请安装 TeXLive 2015
%  编译命令(Windows)：
%      xelatex -shell-escape PMPlanPub.TeX
%
%  注：WBS 章节缺少前置后置图，有兴趣的可补上
%
%%%

%%% Page property
\documentclass[a4paper,11pt]{article}
\usepackage{geometry}
\geometry{left=2.3cm,right=2.3cm,top=2.2cm,bottom=2.2cm}
%\usepackage{indentfirst}

%%% Language spec
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt
\usepackage{xeCJK,fontspec}
\setmainfont{Times New Roman}
\setsansfont{Arial}
\setmonofont{Courier New}
\setCJKmainfont{SimSun}
\setCJKsansfont{SimHei}
\setCJKmonofont{NSimSun}

%%% Table package
\usepackage{array}
\usepackage{longtable}
\newcolumntype{S}{>{\arraybackslash}m{3cm}}
\newcolumntype{L}{>{\arraybackslash}m{5cm}}
\newcolumntype{G}{>{\arraybackslash}m{7cm}}
\newcolumntype{B}{p{0.3\textwidth}}
\newcolumntype{T}{p{0.6\textwidth}}

%%% Feature package
\usepackage{caption}
\usepackage{mpgraphics}



%%% Define the document %%%

\title{Project Management Plan}
\author{Robert, Anne}

\begin{document}

\maketitle
\tableofcontents

\clearpage

\section{Project Summary}
\subsection{Project Overview}

We plan to develop an online medical system for a hospital.

With more and more people prefer to use Internet to search information and do some work that they used to go to hospital.
Many hospital need to improve self regime and standardize their management style to adapt more and more patient demands.
So the system is used to solve some steps that can be done through the Internet.

Patients can use the system to query their information in the hospital. 
The System includes making appointments, news displaying, consulting doctors, patient Information,and back-office operations.
Making appointments are similar to patient make an appointment in hospital. 
It is an important part of the system. 
It's support an entry to go to see doctor and conduct base data information. 
The main page has the doctor brief introduction and some explanation for every department. 
So patients can get some useful information. 
And news are some dynamic information about the hospital and some explanation about health. 

By this system, clients can register and login, make an appointment, search register result or cancel it.
Doctor can use the system to query patients information and registered number to arrange work.
So it can do right decision and improve productivity. 

The system are also useful to manage employee and finance in the hospital. 
It can reduce workload effectively, enhance patient treatment efficient.

\subsection{Program Model}
\begin{center}
\configure[mpggraphic][scale=.75]
\begin{mpdisplay}
input metaobj;
beginfig(1);

newBox.Ce(btex Expert Inquiry\strut etex);
newBox.Cp(btex Reservation Management\strut etex);
newBox.Cc(btex UserData Management\strut etex);
newBox.Cl(btex User Sign in/up\strut etex);

newBox.C(btex Front Operation\strut etex);
newTree.tC(C)(Cp,Cc,Cl,Ce) "Ralign(right)", "treemode(R)";

newBox.Be(btex Expert Management\strut etex);
newBox.Bu(btex User Management\strut etex);
newBox.Bp(btex Reservation Management\strut etex);
newBox.Bb(btex Department Management\strut etex);
newBox.Ba(btex Administrator Only\strut etex);

newBox.B(btex Background Administration\strut etex);
newTree.tB(B)(Be,Bu,Bp,Bb,Ba) "Ralign(right)", "treemode(R)";

newBox.S(btex Reservation System of Hospitals\strut etex);
newTree.tS(S)(tC,tB) "Ralign(right)", "treemode(R)";

tS.c=origin;
drawObj(tS);

endfig;
end
\end{mpdisplay}
\captionof{figure}{Program Model}
\end{center}

\subsection{Project Brief Information}
\begin{center}
\begin{longtable}{|l|l|}
\caption*{Introduction} \\
\hline Project Name        & Hospital Website System \\
\hline Customer            & Hospital \\
\hline Project Start Date  & 2016-03-20 \\
\hline Project End Date    & 2016-06-05 \\
\hline Project Leader (PL) & Robert \\
\hline
\end{longtable}
\end{center}

\subsection{Objectives}
\begin{enumerate}
\item We should develop a system that can be used. 
\item We should use the minimum cost to finish the project.
\item The project must be finished in two months.
\item We can improve our programming skills and complete the final course project.
\item The system is mainly suitable for ordinary users. so the UI must be friendly.
\item Because some patients information may be sensitive, the data security and economics are also important to the system. 
\end{enumerate}

\subsection{Problem}
\begin{enumerate}
\item Our developers are not familiar with business processes.
\item The deadline of the project is urgent.
\item The system users and managers know little about computer , so we must put more time and money to maintain system.
\item Customer has high processing capacity to this project. 
\end{enumerate}

\section{Project Planning}
\subsection{Assumptions}
\begin{enumerate}
\item Training and development are simultaneous.
\item If demand can not be determined at the initial design stage, consider the prototype implementation phase.
\item If the server is down, reseting the initial data.
\item We have corresponding hardware to develop and test our project.
\item If core developers leave, to apply for project delays and proper handover.
\item If the project is shortage of funds, timely financing, reduce unnecessary spending team.
\end{enumerate}

\subsection{Software Process Models}

We use Rational Unified Process (RUP) methodology to develop this project.
The development process will be tailored to match the RUP. 
\begin{center}
\begin{longtable}{|L|L|L|}
\caption*{RUP} \\
\hline Deviations from Standard Process            & Added/Modified/Deleted & Reasons for Deviations \\
\hline Only those use cases that are going to be 
taken up in a particular iteration will be 
elaborated at that point in time                   & Modified               & Iteration-based development is being done \\
\hline A poorly designed user information          & Added                  & Early thoughtless \\
\hline Demand and system design delay two weeks    & Can not be modified    & Missing persons \\
\hline UI can not achieve as design proofs         & Modified               & Improper use of CSS \\
\hline Search feature is not fuzzy search          & Added                  & Lack of appropriate search engine \\
\hline Web mobile terminal adapter poor response   & Modified               & Missing pages for mobile terminals \\
\hline Image loading speed is slower than expected & Modified               & Back-end logic processing complex \\
\hline 
\end{longtable}
\end{center}

\subsection{Schedule}

\begin{center}
\begin{longtable}{|l|l|}
\caption*{The preliminary project schedule} \\
\hline Project Start   & 2016-03-20 \\
\hline Project End     & 2016-06-05 \\
\hline
\end{longtable}

\begin{longtable}{|l|l|l|l|}
\caption*{Detail schedule} \\
\hline Task              & Start time & Finish time & Leader \\
\hline Project Planning  & 2016-03-20 & 2016-03-20  & Robert \\
\hline Requirements      & 2016-03-21 & 2016-03-21  & Anne \\
\hline Design            & 2016-03-22 & 2016-03-31  & Robert \\
\hline Project Implement & 2016-04-01 & 2016-05-20  & Robert \\
\hline Testing           & 2016-05-21 & 2016-05-31  & Anne \\
\hline Submit            & 2016-06-05 & ---         & Robert \\
\hline
\end{longtable}

\begin{longtable}{|r|l|l|l|}
\caption*{Milestones and dividable} \\
\hline Seq Num & Milestone Date   & Milestone                          & Deliverable \\
\hline 1       & 160320 -- 160321 & Requirement analysis               & Document \\
\hline 2       & 160321 -- 160325 & Preliminary plan                   & Document \\
\hline 3       & 160326 -- 160331 & The detailed design of the system  & Document \\
\hline 4       & 160401 -- 160401 & Framework and technology selection & Document \\
\hline 5       & 160401 -- 160410 & Prototype development              & Code \\
\hline 6       & 160410 -- 160520 & product  iterative development     & Code \\
\hline 7       & 160521 -- 160525 & user feedback                      & Document \\
\hline 8       & 160525 -- 160531 & fix system bugs                    & Code \\
\hline 9       & 160601 -- 160603 & Summary of the document            & Document \\
\hline 10      & 160605 -- 160605 & Roll-out and support               & Project Sign-off \\
\hline 
\end{longtable}

\begin{longtable}{|l|r|r|}
\caption*{Phase-wise Effort Estimate} \\
\hline Activity/Phase            & Person-days & Person \\
\hline Requirements              & 3           & 3 \\
\hline Design                    & 20          & 2 \\
\hline Build                     & 60          & 3 \\
\hline Integration testing       & 2           & 1 \\
\hline Regression testing        & 2           & 1 \\
\hline Acceptance testing        & 1           & 1 \\
\hline Project management        & 10          & 1 \\
\hline Configuration  management & 3           & 1 \\
\hline Training                  & 40          & 4 \\
\hline Others                    & 8           & 4 \\
\hline total                     & 149         & --- \\
\hline 
\end{longtable}
\end{center}

\subsection{WBS}
\begin{center}
\configure[mpggraphic][scale=.75]
\begin{mpdisplay}
input metaobj;
beginfig(1);

newBox.ra(btex \begin{tabular}{@{}c@{}} Requirements\\ Analysis\strut \end{tabular} etex);
newBox.rc(btex \begin{tabular}{@{}c@{}} Requirements\\ Capturing\strut \end{tabular} etex);
newBox.mp(btex \begin{tabular}{@{}c@{}} Making\\ Plan\strut \end{tabular} etex);
newBox.r(btex \begin{tabular}{@{}c@{}} Requirment\strut \end{tabular} etex);

newTree.rcra(rc)(ra) "Dalign(bot)";
newTree.mprc(mp)(rcra) "Dalign(bot)";
newTree.rmp(r)(mprc) "Dalign(bot)";

newBox.dd(btex \begin{tabular}{@{}c@{}} Detail\\ Design\strut \end{tabular} etex);
newBox.ad(btex \begin{tabular}{@{}c@{}} Architecture\\ Design\strut \end{tabular} etex);
newBox.da(btex \begin{tabular}{@{}c@{}} Database\\ Design\strut \end{tabular} etex);
newBox.d(btex \begin{tabular}{@{}c@{}} Design\strut \end{tabular} etex);

newTree.addd(ad)(dd) "Dalign(bot)";
newTree.ddaad(d)(da,addd) "Dalign(bot)";

newBox.co(btex \begin{tabular}{@{}c@{}} Coding\strut \end{tabular} etex);
newBox.bf(btex \begin{tabular}{@{}c@{}} Build System\\ Framework\strut \end{tabular} etex);
newBox.pr(btex \begin{tabular}{@{}c@{}} Programing\strut \end{tabular} etex);

newTree.bfco(bf)(co) "Dalign(bot)";
newTree.prbf(pr)(bfco) "Dalign(bot)";

newBox.at(btex \begin{tabular}{@{}c@{}} Acceptance\\ Test\strut \end{tabular} etex);
newBox.st(btex \begin{tabular}{@{}c@{}} System\\ Test\strut \end{tabular} etex);
newBox.it(btex \begin{tabular}{@{}c@{}} Integrated\\ Test\strut \end{tabular} etex);
newBox.ut(btex \begin{tabular}{@{}c@{}} Unit\\ Testing\strut \end{tabular} etex);
newBox.t(btex \begin{tabular}{@{}c@{}} Testing\strut \end{tabular} etex);

newTree.stat(st)(at) "Dalign(bot)";
newTree.itst(it)(stat) "Dalign(bot)";
newTree.utit(ut)(itst) "Dalign(bot)";
newTree.tut(t)(utit) "Dalign(bot)";

newBox.pj(btex \begin{tabular}{@{}c@{}} Project\strut \end{tabular} etex);

newTree.pjt(pj)(rmp,ddaad,prbf,tut) "Dalign(bot)";

pjt.c=origin;
drawObj(pjt);
endfig;
end
\end{mpdisplay}
\captionof{figure}{Graph of Planning}
\end{center}

\begin{center}
\begin{longtable}{|r|l|r|l|l|r|}
\caption*{WBS} \\
\hline No. & Activity               & Duration    & Start      & Finish     & Pre-task \\
\hline 1   & +online book system    & 75          & 2016-03-20 & 2016-06-05 & --- \\
\hline 2   & +software planning     & 1           & 2016-03-20 & 2016-03-21 & --- \\
\hline 3   & program planning       & 0.5         & 2016-03-20 & 2016-03-20 & --- \\
\hline 4   & review planing         & 0.5         & 2016-03-21 & 2016-03-21 & --- \\
\hline 5   & +requirements analysis & 4           & 2016-03-22 & 2016-03-25 & 2   \\
\hline 6   & demand specification   & 2           & 2016-03-22 & 2016-03-24 & --- \\
\hline 7   & interface design       & 1           & 2016-03-23 & 2016-03-24 & --- \\
\hline 8   & demand validation      & 1           & 2016-03-25 & 2016-03-26 & --- \\
\hline 9   & +design                & 6           & 2016-03-26 & 2016-03-31 & 5   \\
\hline 10  & general design         & 2           & 2016-03-26 & 2016-03-27 & --- \\
\hline 11  & specific design        & 2           & 2016-03-28 & 2016-03-29 & --- \\
\hline 12  & validation             & 2           & 2016-03-30 & 2016-03-31 & --- \\
\hline 13  & +develop               & 50          & 2016-04-04 & 2016-05-20 & 2.5 \\
\hline 14  & coding                 & 40          & 2016-04-01 & 2016-05-20 & --- \\
\hline 15  & re-checking            & 10          & 2016-05-01 & 2016-05-10 & --- \\
\hline 16  & unit testing           & 45          & 2016-04-01 & 2016-05-20 & --- \\
\hline 17  & +testing               & 10          & 2016-05-21 & 2016-05-31 & 13  \\
\hline 18  & integration testing    & 5           & 2016-05-21 & 2016-05-25 & --- \\
\hline 19  & system testing         & 5           & 2016-05-26 & 2016-05-31 & --- \\
\hline 20  & +software acceptance   & 5           & 2016-06-01 & 2016-06-05 & 13  \\
\hline 21  & software delivery      & 1           & 2016-06-05 & 2016-06-05 & --- \\
\hline 
\end{longtable}
\end{center}

\subsection{Resource}
\begin{center}
\begin{longtable}{|l|l|}
\caption*{Resource Management} \\
\hline Resource  & Number \\
\hline Human     & 4 persons \\
\hline Equipment & 5 computers and 1 server \\
\hline
\end{longtable}

\begin{longtable}{|l|l|}
\caption*{Development Environment} \\
\hline Hardware & Software \\
\hline Intel PC & Tomcat Server \\
\hline Intel PC & SpringMVC \\
\hline Mac Pro  & AngularIDE \\
\hline
\end{longtable}

\begin{longtable}{|l|r|}
\caption*{Resource Requirement} \\
\hline Resource          & Required \\
\hline PCs with 16GB RAM & 2 \\
\hline MySQL             & 2 \\
\hline SpringMVC         & 2 \\
\hline WebStormIDE       & 3 \\
\hline EclipseIDE        & 3 \\
\hline
\end{longtable}
\end{center}

\section{People management}
\subsection{Team Management}
\begin{center}
\begin{longtable}{|l|l|r|l|}
\caption*{Team Construction} \\
\hline Name   & Role          & Desired & Date \\
\hline Robert & PL            & 1       & 160320 \\
\hline Robert & Module leader & 1       & 160320 \\
\hline Robert & Developers    & 2       & 160320 \\
\hline Anne   & Tester        & 1       & 160521 \\
\hline Robert & Total         & 4       & --- \\
\hline Anne   & Total         & 1       & --- \\
\hline
\end{longtable}

\begin{longtable}{|l|r|}
\caption*{People's Skill and Experience} \\
\hline Domain        & Total \\
\hline Java          & 4 \\
\hline Hibernate     & 4 \\
\hline HTML, CSS, JS & 3 \\
\hline SpringMVC     & 3 \\
\hline AngularJS     & 2 \\
\hline MySQL         & 4 \\
\hline
\end{longtable}
\end{center}

\subsection{Responsibility of Role}
\begin{center}
\begin{longtable}{|S|T|}
\caption*{Roles and Responsibilities} \\

\hline Role & Responsibilities \\

\hline Business Manager (BM) &
    \begin{itemize}
    \item Resolve escalated issues
    \item Review project status
    \item Participate in critical technical reviews
    \end{itemize} \\
    
\hline Customer &
    \begin{itemize}
    \item Review design
    \item Resolve escalated issues
    \item Acceptance test planning and testing
    \end{itemize} \\
    
\hline Account Manager (AM) &
    \begin{itemize}
    \item Customer satisfaction
    \item Business growth
    \item Project financial plan
    \item Interface with sales and marketing
    \item Training-related issues
    \item Employee-related issues
    \end{itemize} \\
    
\hline Project Manager (PM) &
    \begin{itemize}
    \item Project planning and scheduling
    \item Design
    \item Customer interaction
    \item Reviews
    \item Testing
    \item Reporting
    \item Task assignment and tracking
    \item Interact with software quality adviser from SEPG
    \item Ensure delivery as per contract
    \item Interface with other departments as per need
    \item Ensure open issues/customer complaints are closed properly
    \item Ensure project members are adequately trained
    \end{itemize} \\
    
\hline Module Leader (ML) &
    \begin{itemize}
    \item Design
    \item Development
    \item Testing
    \item Reporting
    \end{itemize} \\
    
\hline Defect Prevention (DP) Team &
    \begin{itemize}
    \item Spread awareness in the team on defects and their prevention
    \item Analyze defect data
    \item Identify methods to reduce defect injection
    \end{itemize} \\
    
\hline Developer (DV) &
    \begin{itemize}
    \item Detail design for use cases
    \item Development
    \item Unit testing and integration testing
    \end{itemize} \\
    
\hline Configuration Controller (CC) &
    \begin{itemize}
    \item Prepare the CM plan
    \item Manage the configuration as per the CM plan
    \end{itemize} \\
    
\hline Software Quality Adviser (SQA) from the SEPG &
    \begin{itemize}
    \item Process consultancy
    \item Quality assurance (audits)
    \item Install measurement tools and train project personnel
    \item Participate in reviews of project plan and processes as necessary
    \end{itemize} \\
    
\hline
\end{longtable}
\end{center}

\subsection{Team Communication}
In order to make the project goes well , we plan to have team meeting once a week.

At the team meeting, every teammate should report their work schedule, problems or ideas.

Every Monday, project manager should report to business manager about the project and report to the customer about the schedule. 

\begin{center}
\begin{longtable}{|l|l|}
\caption*{Team Communication} \\
\hline Activity                   & Frequency \\
\hline Team meeting               & Once a week \\
\hline Report To Business manager & Weekly on Monday via e-mail \\
\hline Report To Customer         & Weekly on Monday \\
\hline 
\end{longtable}
\end{center}

\subsubsection{Report to the Customer}
\begin{enumerate}
\item Milestones reports and weekly status reports.
\item Issues requiring clarifications and Escalation.
\end{enumerate}

\subsubsection{Report to the BM}
\begin{enumerate}
\item Milestones and weekly status reports.
\item Customer feedback.
\item Major changes in plan.
\item Escalation and Issues requiring attention.
\item Number of requirement changes and estimated effort for them.
\end{enumerate}

\section{Cost Estimation}
Total cost is made up of direct cost and indirect cost.
Direct cost consist of development cost and management cost and quality cost.
Indirect cost consist of general cost, training cost, employee welfare, service cost, etc.

In this project, our main development cost is the money to pay employees.
The equipment cost will not be calculated in indirect cost.

\subsection{Development Cost}
We suppose that one person's wage is \(50/day\).
We can take from table Phase-wise Effort Estimate that total workloads is \(149\) days.
So the development cost is \(149 \times 100\).

\subsection{Administration Cost}
According to normal circumstances,
\[
Administration Cost = Development Cost \times 20\%
\]

\subsection{Direct Cost}
\[
Direct Cost = Development Cost + Administration Cost
\]

\subsection{Indirect Cost}
Indirect cost include training cost, traveling expenses, utilities, staff welfare, service cost, etc.
Based on past experience,
\[
Indirect Cost = Direct Cost \times 25\%
\]

\subsection{Total Cost}
\[
Total Cost = Direct Cost + Indirect Cost
\]

\begin{center}
\begin{longtable}{|l|r|}
\caption*{Cost} \\
\hline Class               & Cost \\
\hline Development Cost    & 14900 \\
\hline Administration Cost & 2980 \\
\hline Direct Cost         & 17880 \\
\hline Indirect Cost       & 4470 \\
\hline Total Cost          & 22350 \\
\hline 
\end{longtable}
\end{center}

\subsection{Ways to Reduce the Cost}
\begin{enumerate}
\item Every teammate plays more than one roles 
\item We studied by Internet and free books. so we can reduce the cost of training
\item We use the original web site development environment for development, reducing the cost of software.
\item We use convenient development framework, reducing development and maintenance time of developers
\item We pay much attention to testing and test frequently
\end{enumerate}

\subsection{Profit Predict}
We think the risk profit rate is \(70\%\) (including risk fund \(10\%\), profit \(55\%\), Taxes \(5\%\)).

So we can calculate the price of the software should be \(22270 \times 2 = 44540\) yuan.

So the profit predict is about \(12248\) yuan. 

\section{Risk Management}
\begin{center}
\begin{longtable}{|L|r|r|S|}
\caption*{Risk Management} \\
\hline Risks                                     & Probability & risk assessment & Mitigation Plan \\
\hline The project objectives are not clearly    & 0.5         & 8               & Make sure the objective clearly \\
\hline Not have the Project Feasibility Analysis & 0.5         & 10              & Take enough time to analysis and study \\
\hline The demands change frequently             & 0.6         & 8               & Communicate with customer well \\
\hline Design deviated from the customer's 
demands or miss some important functions         & 0.4         & 10              & Review the design result \\
\hline Developer's ability are inadequate or 
misunderstand the customer's demands             & 0.6         & 9               & Training or Substitution \\
\hline Developers are leaving                    & 0.3         & 10              & Sign  the contract  with employee \\
\hline Not have testing play                     & 0.2         & 5               & Realize the review testing plan \\
\hline Find material weakness after testing      & 0.6         & 8               & Use Distributed Testing \\
\hline Tester is lack of experience              & 0.7         & 2               & Select experienced tester or training \\
\hline Can't solve the problems after testing    & 0.6         & 6               & Developers consultation \\
\hline Have many problems when running project   & 0.8         & 4               & Run the project partly \\
\hline Customer add demand suddenly              & 0.8         & 4               & Communicate with customer and make sure the project scope \\
\hline Important data loss                       & 0.2         & 10              & Make the backup data \\
\hline Customer can't use the project easily     & 0.4         & 2               & Make detailed user guide or train user on software using \\
\hline 
\end{longtable}
\end{center}

\section{Quality Plan}
We have some measures to improve the project quality The AM/PL is responsibility to get the customer feedback, 
organize the customer's demands, and submit the feedback file to BM.
If customer have some complaints, The AM/PL should track them and note them into customer complaint file. 

When schedule changes every time, it must be agreed by the BM. 
If some significant changes are made or Milestone reports have been submitted, they must reviewed by senior management.

During the project, their are some review items that should be review. they are shown in the diagrams below.

\begin{center}
\begin{longtable}{|L|L|L|}
\caption*{Quality Plan} \\
\hline Review Point                                                & Review Item                      & Type of Review \\
\hline End of project planning                                     & Project plan                     & Group review \\
\hline End of project planning                                     & DCS set up                       & SQA review \\
\hline End of project planning                                     & Project schedule                 & SQA review \\
\hline End of project planning                                     & CM Plan                          & Group review \\
\hline End of 90\% of requirements (This should be at the end of 
first elaboration iteration)                                       & Business analysis and 
                                                                     requirements specification 
                                                                     document, Use case catalog       & Group review \\
\hline End of 90\% design (This should be at the end of second 
elaboration iteration)                                             & Design document, object model    & Group review \\
\hline Beginning of each iteration                                 & Iteration plans                  & One-person review \\
\hline End of detailed design                                      & Complex/first time generated 
                                                                     program specs incl, test cases, 
                                                                     interactive diagrams             & Group review \\
\hline After coding for first few programs                         & Code                             & Group review \\
\hline After self-testing of a process                             & Code                             & One-person review \\
\hline End of unit test plan                                       & Unit test plan                   & One-person review \\
\hline Beginning of integration test                               & Integration test plan            & Group review \\
\hline
\end{longtable}
\end{center}

\end{document}
